### 2018-10-03 paper/paper.tex
added references

% \usepackage[table]{xcolor}
% \usepackage{xcolor}
% \usepackage[utf8x]{inputenc}
% \usepackage{listings}
% \usepackage{amsmath,amssymb}
% \usepackage[noend]{algpseudocode}
% \usepackage{stmaryrd}
% \usepackage{listings}
% \usepackage{algorithm}
% \usepackage{array}
% \usepackage{textcomp}
% \usepackage{pifont}
% \usepackage{bbding}
% \usepackage{comment}
% \usepackage{graphicx}
% \usepackage{paper}
% \usepackage[svgpath=figures/]{svg}
% \usepackage[labelfont=bf]{caption}
% \captionsetup[table]{skip=5pt}

@@

@@

@@

@@

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

% \usepackage[table]{xcolor}
% \usepackage{xcolor}
% \usepackage[utf8x]{inputenc}
% \usepackage{listings}
% \usepackage{amsmath,amssymb}
% \usepackage[noend]{algpseudocode}
% \usepackage{stmaryrd}
% \usepackage{listings}
% \usepackage{algorithm}
% \usepackage{array}
% \usepackage{textcomp}
% \usepackage{pifont}
% \usepackage{bbding}
% \usepackage{comment}
% \usepackage{graphicx}
\usepackage{paper}
% \usepackage[svgpath=figures/]{svg}
% \usepackage[labelfont=bf]{caption}
% \captionsetup[table]{skip=5pt}

@@

Lead Time Syndrome (LTS)

@@

In this section we present a formalisation of the \LTS{}. It is straightforward to implement the
presented methods to establish a \LTS{} detection system. We follow the notation established
by~\cite{selccuk2013adaptive}.

\subsection{Single-Stage Manufacturing System}
\label{subsec:Single-Stage_Manufacturing_System}

Consider a single product one-stage manufacturing system that releases orders from the order pool
into the production system by an external mechanism. We denote the demand rate at time
$t \geqslant 0$ as $\dr{t}$, and the demand for the item during the period defined by timestamps
$t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$. Similarly we denote the order release
rate as $\rr{t}$ and the releases within a period as $\ri{t_{1}}{t_{2}}$. Usually

\begin{definition}

  The overall queue length

\end{definition}

@@

\subsection{Multi-Stage Manufacturing System}
\label{subsec:Multi-Stage_Manufacturing_System}

We now lift the established metric to multi-stage manufacturing systems.

@@

\end{document}

% --------------------
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
